IGAS Project

### 2023-10-29 Appendix/E1_Appendix.qmd
adjust appendices

### Appendix - Project 2 - Experiment 1

@@

## E1 Appendix

### Posterior Predictive Distributions

```{r}
#| label: fig-post-pred
#| fig-cap: Posterior Predictive distributions for Deviation and Vx. Posterior Draws in Blue, colored lines are empirical data. 
#| fig-subcap: ["Posterior Predictive Distribution - Deviation", "Posterior Predictive Distribution - X Velocity"]
#| fig-width: 13
#| fig-height: 12

vx_pred <- 
  posterior_predict(e1_vxBMM, ndraws = 500) |> 
  array_branch(margin=1) |> 
   map_dfr( 
    function(yrep_iter) {
      test  |>
        mutate(vx_pred = yrep_iter)
    },
    .id = 'iter'
  ) |>
  mutate(iter = as.numeric(iter))

@@

@@

### Empirical vs. Predicted

```{r}
#| label: fig-empVsPred
#| fig-cap: Bayesian Mixed Model predictions vs. Empirical Predictions - X velocity
#| fig-height: 15
#| fig-width: 12

@@

### Different Aggregations

```{r fig.width=14, fig.height=13}
#| label: fig-empirical-vxGrp
#| fig-cap: E1. Distribution of vx at Participant and Trial level
#| fig-width: 13
#| fig-height: 14

epId <- vx_pred  |>
  filter(iter < 2)  |> group_by(id,condit,vb) |>
  summarise(vx=median(vx)) |>
  ggplot(aes(x=vb,y=vx,fill=condit)) + 
  geom_flat_violin(aes(fill=condit), position = position_nudge(x = 0.1, y = 0),
                   adjust = 1.5,trim = FALSE, alpha = .5, colour = NA) +
  geom_point(aes(x = as.numeric(vb) - 0.15, col=condit),
             position = position_jitter(width = 0.05, height = 0),
             size = 1, shape = 20, alpha=.7) +
  geom_boxplot(aes(x=vb,y=vx,fill=condit),
               outlier.shape = NA,
               alpha = 0.5, width = 0.1) +
  geom_hline(yintercept = 0,
             linetype = 'dashed',
             color = 'red',
             size = 0.4) + 
  coord_flip() + ggtitle("Empirical Vx - Subject level averaging")

epTrial <- vx_pred  |>
  filter(iter < 2)  |> group_by(id,condit,vb) |>
  ggplot(aes(x=vb,y=vx,fill=condit)) + 
  geom_flat_violin(aes(fill=condit), position = position_nudge(x = 0.1, y = 0),
                   adjust = 1.5,trim = FALSE, alpha = .5, colour = NA) +
  geom_point(aes(x = as.numeric(vb) - 0.15, col=condit),
             position = position_jitter(width = 0.05, height = 0),
             size = .5, shape = 20, alpha=.7) +
  geom_boxplot(aes(x=vb,y=vx,fill=condit),
               outlier.shape = NA,
               alpha = 0.5, width = 0.1) +
  geom_hline(yintercept = 0,
             linetype = 'dashed',
             color = 'red',
             size = 0.4) + 
  coord_flip() + ggtitle("Empirical Vx - Raw Trial") +
   theme(axis.title.y=element_blank(),
        axis.text.y=element_blank())

epId + epTrial
```

```{r fig.width=14, fig.height=13}
#| label: fig-empirical-distGrp
#| fig-cap: E1. Distribution of Vx  at Participant and Trial level
#| fig-width: 13
#| fig-height: 14

@@

epTrial <- dist_pred  |>
  filter(iter < 2)  |> group_by(id,condit,vb) |>
  ggplot(aes(x=vb,y=dist,fill=condit)) + 
  geom_flat_violin(aes(fill=condit), position = position_nudge(x = 0.1, y = 0),
                   adjust = 1.5,trim = FALSE, alpha = .5, colour = NA) +
  geom_point(aes(x = as.numeric(vb) - 0.15, col=condit),
             position = position_jitter(width = 0.05, height = 0),
             size = .5, shape = 20, alpha=.7) +
  geom_boxplot(aes(x=vb,y=dist,fill=condit),
               outlier.shape = NA,
               alpha = 0.5, width = 0.1) +
  geom_hline(yintercept = 0,
             linetype = 'dashed',
             color = 'red',
             size = 0.4) + 
  coord_flip() + ggtitle("Empirical Deviation - Raw Trial") +
   theme(axis.title.y=element_blank(),
        axis.text.y=element_blank())

epId + epTrial
```

>>>>

@@

#### Posterior Predictive Distributions

```{r}
#| label: fig-post-pred-dist
#| fig-cap: Posterior Predictive distributions for Absolute Deviance. Posterior Draws in Blue, colored lines are empirical data. 
#| fig-width: 11
#| fig-height: 9

@@

```{r}
#| label: fig-post-pred-vx
#| fig-cap: Posterior Predictive distributions for Vx. Posterior Draws in Blue, colored lines are empirical data. 
#| fig-width: 11
#| fig-height: 7
vx_pred <- 
  posterior_predict(e1_vxBMM, ndraws = 500) |> 
  array_branch(margin=1) |> 
   map_dfr( 
    function(yrep_iter) {
      test  |>
        mutate(vx_pred = yrep_iter)
    },
    .id = 'iter'
  ) |>
  mutate(iter = as.numeric(iter))

@@

#### Empirical vs. Predicted

```{r}
#| label: fig-empVsPred
#| fig-cap: Bayesian Mixed Model predictions vs. Empirical Predictions - X velocity
#| fig-height: 12
#| fig-width: 11

@@

```{r}

#### Different Aggregations

```{r}
#| label: fig-empirical-distGrp1
#| fig-cap: E1. Distribution of Vx  at Participant level
#| fig-width: 12
#| fig-height: 10

@@

epId 
```

```{r}
#| label: fig-empirical-distGrp2
#| fig-cap: E1. Distribution of Vx at Trial level
#| fig-width: 12
#| fig-height: 10
epTrial <- dist_pred  |>
  filter(iter < 2)  |> group_by(id,condit,vb) |>
  ggplot(aes(x=vb,y=dist,fill=condit)) + 
  geom_flat_violin(aes(fill=condit), position = position_nudge(x = 0.1, y = 0),
                   adjust = 1.5,trim = FALSE, alpha = .5, colour = NA) +
  geom_point(aes(x = as.numeric(vb) - 0.15, col=condit),
             position = position_jitter(width = 0.05, height = 0),
             size = .5, shape = 20, alpha=.7) +
  geom_boxplot(aes(x=vb,y=dist,fill=condit),
               outlier.shape = NA,
               alpha = 0.5, width = 0.1) +
  geom_hline(yintercept = 0,
             linetype = 'dashed',
             color = 'red',
             size = 0.4) + 
  coord_flip() + ggtitle("Empirical Deviation - Raw Trial") +
   theme(axis.title.y=element_blank(),
        axis.text.y=element_blank())

epTrial
```

### 2023-10-29 Appendix/IGAS-Supplemental.qmd
adjust appendices

### First vs. second half of testing stage
```{r,fig.height=7,fig.width=8}

@@

# 
 #testSplit2 %>% anova_test(dv=MeanScaledDev,between=conditType,within = c(testHalfSbj),wid=sbjCode,type=3)
 #testSplit %>% anova_test(dv=MeanTargetDistance,between=conditType,covariate=testHalfSbj,within=(positionX),wid=sbjCode)
# testSplit %>% lmer(MeanTargetDistance ~ conditType*testHalfSbj + (1|sbjCode)+(1+testHalfSbj|positionX),data=.) %>% summary()

# testSplit %>% anova_test(dv=MeanTargetDistance,between=conditType,within=positionX,wid=sbjCode,type=3)
# 
# print("Testing End - Testing Start Comparison")
# tsw %>% anova_test(dv=endMinusStart,between=conditType,within=positionX,wid=sbjCode,type=3)
# tsw2 %>% anova_test(dv=endMinusStartScaled,between=conditType,wid=sbjCode,type=3)
# 
# print("2nd Half of testing only comparison")
# testSplit %>% filter(testHalfSbj=="2nd-Half")%>%  anova_test(dv=MeanTargetDistance,between=conditType,within=(positionX),wid=sbjCode)
# testSplit2 %>% filter(testHalfSbj=="2nd-Half")%>%  anova_test(dv=MeanScaledDev,between=conditType,wid=sbjCode,type=3)
# 
# testSplit2 %>% filter(testHalfSbj=="2nd-Half")%>% group_by(conditType) %>% get_summary_stats(type = "mean_sd")

@@

e2TestFits %>% ggplot(aes(x=conditType,y=Asymptote.Minus.Start,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ 
  stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+facet_grid(~positionX)+ggtitle("e2 testing (asymptote - start performance)  ")
```

@@

# exp1Transfer3 %>% ggplot(aes(x=positionX,y=MeanTargetDeviance,group=conditType2,fill=conditType2))+geom_bar(stat="summary",position=dodge)+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+theme_classic()+scale_x_discrete(name="Testing Location",breaks=e1Pos,labels=e1Labels)

# exp1Transfer3 %>% ggplot(aes(x=positionX,y=meanRelativeDist,group=conditType2,fill=conditType2))+geom_bar(stat="summary",position=dodge)+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+theme_classic()+scale_x_discrete(name="Testing Location",breaks=e1Pos,labels=e1Labels)+ggtitle("Experiment 1 Test -Relative Distance")
# 
# 
# 
# exp1Transfer3 %>% ggplot(aes(x=positionX,y=MeanTargetDeviance,group=conditType2,fill=conditType2))+geom_bar(stat="summary",position=dodge)+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+theme_classic()+scale_x_discrete(name="Testing Location",breaks=e1Pos,labels=e1Labels)+facet_grid(.~devianceDirection)

@@

# exp2Transfer3 %>% ggplot(aes(x=ThrowPosition,y=meanRelativeDist,group=conditType2,fill=conditType2))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+theme_classic()+ggtitle("Experiment 2 Test - Relative Distance")
# 
# exp2Transfer3 %>% ggplot(aes(x=ThrowPosition,y=MeanTargetDeviance,group=conditType2,fill=conditType2))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+theme_classic()+facet_grid(.~devianceDirection)+ggtitle("Absolute Dist - Split by Over/Under")

@@

# 
# exp2Transfer4 %>% ggplot(aes(x=positionX,y=MeanTargetDeviance,group=Group2,fill=Group2))+geom_bar(stat="summary",position=position_dodge(),fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=position_dodge())+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Position"))+theme(legend.title.align=.25)+theme_classic()+facet_grid(.~devianceDirection)+ggtitle("Absolute Dist - Split by Over/Under")
# 
# 
# exp2Transfer4 %>% ggplot(aes(x=positionX,y=meanRelativeDist,group=Group2,fill=Group2))+geom_bar(stat="summary",position=position_dodge(),fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=position_dodge())+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Position"))+theme(legend.title.align=.25)+theme_classic()+facet_grid(.~devianceDirection)+ggtitle("Experiment 2 Test - Relative Distance")

# 
# t= exp2Transfer3  %>% 
#   mutate(Condition=conditType2) %>%
#   group_by(Condition,positionX) %>% 
#   summarise(Mean.signed=round(mean(meanRelativeDist),2),
#             sd.signed=round(sd(meanRelativeDist),2),
#             msds=paste(Mean.signed,"(",sd.signed,")",sep=""),
#             .groups="keep") %>% ungroup() %>%
#    select(-Mean.signed,-sd.signed) %>% 
#   pivot_wider(names_from = positionX,values_from=c(msds)) %>% as.data.frame() %>%stargazer(.,type="text",summary=FALSE,rownames = FALSE)
#

@@

#### Experimenet 1 - intermittent testing
```{r,fig.width=9}
# first 3 trials - 1 throw from 610, 760 and 910
# interleaved every 20 trials, 2 throws from 610, 760, 910
# 10 full intermittent tests (6 trials each), plus 3 at beginning = 63 total per subject. 
#[1] 0  2  3  5  6  8  9  11 12 14 15 17 18 20 21 23 24 26 27 29 30
# First final testing trial is 264. So 1-263 = training and intermittent testing. 
# 
# intTest.third <- exp1.inter %>% filter(intStage!="int1")%>% group_by(sbjCode,conditType,stage,intStage,positionX) %>%
#   summarise(MeanTargetDistance=mean(AbsDistFromCenter,trim=.05)) %>% group_by(sbjCode,conditType,stage,positionX) %>%
#   summarise(MeanTargetDistance=mean(MeanTargetDistance))
# 
# intTest.third %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
#   geom_bar(aes(group=stage,fill=stage),stat="summary",fun=mean,position=dodge)+
#   facet_wrap(~conditType,ncol=2)+
#   stat_summary(aes(x=positionX,group=stage),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+
#   ylab("Mean Distance From Center Of Target")+
#   xlab("Throw Location")+theme(plot.title = element_text(hjust = 0.5))+
#   guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)
# 
# intTest.half %>% anova_test(dv=MeanTargetDistance,between=conditType,within=trainHalf,covariate=positionX,wid=sbjCode)
# intTest.half %>% anova_test(dv=MeanTargetDistance,between=conditType,within=c(trainHalf,positionX),wid=sbjCode)

@@

# intTest.half <- exp1.inter %>%filter(AbsDistFromCenter<1550)%>% 
#   group_by(sbjCode,conditType,trainHalf,positionX) %>%
#   summarise(MeanTargetDistance=mean(AbsDistFromCenter,trim=.01))

@@

# exp1TrainTrials %>% filter(AbsDistFromCenter<1000) %>% ggplot(aes(x=trainIndex,y=AbsDistFromCenter,group=conditType2)) +geom_point()+geom_smooth(method="lm",se=FALSE) +facet_grid(~positionX)

@@

# fit to testing performance averaged across positions
```{r}
e2Fits.AggPos <- readRDS(here::here('data/IGAS-e2Fits.AggPos-April_12.rds'))

e2Fits.AggPos %>% ggplot(aes(x=Group,y=pStart,fill=Group))+geom_bar(stat="summary",position=dodge,fun="mean")+ 
  stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ggtitle("experiment 2 - starting performance per position")

e2Fits.AggPos %>% ggplot(aes(x=Group,y=pAsym,fill=Group))+geom_bar(stat="summary",position=dodge,fun="mean")+ 
  stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ggtitle("e2 testing performance asymptote per position ")

e2Fits.AggPos %>% ggplot(aes(x=Group,y=pRate,fill=Group))+geom_bar(stat="summary",position=dodge,fun="mean")+ 
  stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ggtitle("e2 testing performance asymptote per position ")

@@

e2TestFits %>% ggplot(aes(x=conditType,y=pStart,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ 
  stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+facet_grid(~positionX)+ggtitle("experiment 2 - starting performance per position")

@@

e2TestFits %>% ggplot(aes(x=conditType,y=pAsym,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ 
  stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+facet_grid(~positionX)+ggtitle("e2 testing performance asymptote per position ")

>>>>

### First vs. second half of testing stage
```{r}

@@

@@

e2TestFits %>% ggplot(aes(x=conditType,y=Asymptote.Minus.Start,fill=conditType))+
  geom_bar(stat="summary",position=dodge,fun="mean")+ 
  stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+
  facet_grid(~positionX)+ggtitle("e2 testing (asymptote - start performance)") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))

@@

@@

@@

@@

#### Experimenet 1 - intermittent testing
```{r}

@@

@@

@@

#### fit to testing performance averaged across positions
```{r}
e2Fits.AggPos <- readRDS(here::here('data/IGAS-e2Fits.AggPos-April_12.rds'))

e2Fits.AggPos %>% ggplot(aes(x=Group,y=pStart,fill=Group))+
  geom_bar(stat="summary",position=dodge,fun="mean")+ 
  stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+
  ggtitle("experiment 2 - starting performance per position") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))

e2Fits.AggPos %>% ggplot(aes(x=Group,y=pAsym,fill=Group))+
  geom_bar(stat="summary",position=dodge,fun="mean")+ 
  stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+
  ggtitle("e2 testing performance asymptote per position ") +
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))

e2Fits.AggPos %>% ggplot(aes(x=Group,y=pRate,fill=Group))+
  geom_bar(stat="summary",position=dodge,fun="mean")+ 
  stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+
  ggtitle("e2 testing performance asymptote per position ") +
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))

@@

e2TestFits %>% ggplot(aes(x=conditType,y=pStart,fill=conditType))+
  geom_bar(stat="summary",position=dodge,fun="mean")+ 
  stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+
  facet_grid(~positionX)+ggtitle("experiment 2 - starting performance per position") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))

@@

e2TestFits %>% ggplot(aes(x=conditType,y=pAsym,fill=conditType))+
  geom_bar(stat="summary",position=dodge,fun="mean")+ 
  stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+
  facet_grid(~positionX)+ggtitle("e2 testing performance asymptote per position ") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
